\chapter{Introduction}
\section{Purpose}
The primary purpose of the cow pose estimation project is to develop a comprehensive and accurate system for monitoring and analyzing the posture and movements of cattle in agricultural settings. By leveraging advanced computer vision techniques, the project aims to address the following key objectives: Enhancing Livestock Welfare, Optimizing Farm Management, Supporting Research and Innovation.
\section{Intended Audience}
This project targets researchers and agricultural scientists engaged in livestock management, as well as professionals in computer vision, machine learning, and artificial intelligence interested in applying their skills to agricultural contexts. Additionally, students and enthusiasts exploring interdisciplinary studies at the intersection of technology and agriculture may find the project's outcomes and methodologies valuable.
\section{Project Scope}
The project encompasses the development and implementation of a cow pose estimation system using deep learning techniques. Key components of the project include data collection and annotation, model training and evaluation, and deployment of the trained model for real-world applications. The scope also extends to exploring data augmentation strategies, optimizing model performance, and assessing the system's accuracy and reliability in diverse agricultural environments. Furthermore, considerations for scalability, usability, and integration with existing livestock management systems will be addressed to ensure the practicality and effectiveness of the proposed solution.
\section{Definitions, Acronyms, \& Conventions}
\begin{table}[h]
    \centering
    \begin{tabular}{|c|p{12cm}|}
        \hline
        \textbf{Term} & \textbf{Definition}\\
        \hline
        YOLO & You Only Look Once\\
        \hline 
        PIL & Python Imaging Library\\
        \hline  
        bbox & Bounding Box\\
        \hline  
        Json & JavaScript Object Notation\\
        \hline  
        Ultralytics & develop and maintain popular tools and libraries, including models for object detection and image classification, such as YOLO (You Only Look Once)\\
        \hline  
        Open-cv &  open-source computer vision and machine learning software library designed to provide a common infrastructure for various applications in the field of computer vision.\\
        \hline  
        
        
    \end{tabular}
\end{table}