\chapter{Summary \& Future Work}
\section{Research Efforts}
The majority of the project's time was dedicated to research, particularly due to the novelty of the topic and its complexities. As a newcomer to the field of pose estimation, extensive time was spent on understanding the underlying principles, exploring relevant literature, and familiarizing myself with computer vision and machine learning. 

Additionally, quite some time was invested in investigating available datasets, and understanding data preprocessing techniques.

Moving forward, the knowledge acquired during this research phase will not only help immensely to continue and shape the project's trajectory but also with anything related to pose estimation and computer vision.
\section{Overall}
Throughout the project duration,  Significant progress has been made in the research and learning of pose estimation, ultralytics, and computer vision. Leveraging cutting-edge techniques in computer vision and machine learning, we have developed a system capable of identifying and tracking key anatomical landmarks on cows. Despite encountering challenges, such as data preprocessing complexities and model optimization intricacies, the project has successfully implemented core functionalities for accurate cow pose estimation.

However, it's important to note that the model still does not consistently yield accurate results. Moving forward, the next step would involve data augmentation techniques to enhance the model's performance. These techniques, such as rotating images and their corresponding coordinates, flipping or reflecting images, and augmenting the dataset, have the potential to improve the model's accuracy and generalization capabilities.

Regrettably, due to time constraints, further exploration and refinement of these techniques must be postponed. Nonetheless, these plans remain on the agenda for future iterations of the project. With additional time and resources, the project can continue to evolve, paving the way for more accurate and reliable cow pose estimation systems in the agricultural domain.

